---
title: 'Homework 4: Bags, Forests, Boosts, oh my'
author: "Your Name Goes Here"
date: "2/28/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libs, include=FALSE}
library(tidyverse)
library(broom)
library(glmnet)
library(caret)
library(ISLR)
library(janitor)
library(stringr)
library(rsample)
library(caret)
library(MASS)
library(randomForest)
library(ISLR)
library(tree)
library(gbm)
```

## Problem 1

Problem 7 from Chapter 8 in the text. To be specific, please use a sequence of
`ntree` from 25 to 500 in steps of 25 and `mtry` from 3 to 9 for by 1. 

In the lab, we applied random forests to the Boston data using mtry=6 and using ntree=25 and ntree=500. Create a plot displaying the test error resulting from random forests on this data set for a more comprehensive range of values for mtry and ntree. You can model your
plot after Figure 8.10. Describe the results obtained.

## Answer 1
```{r}
set.seed(1)
train <- sample(1:nrow(Boston), nrow(Boston) / 2)
Boston.train <- Boston[train, -14]
Boston.test <- Boston[-train, -14]
Y.train <- Boston[train, 14]
Y.test <- Boston[-train, 14]
rf.boston1 <- randomForest(Boston.train, y = Y.train, xtest = Boston.test, ytest = Y.test, mtry = ncol(Boston) - 1, ntree = 500)
rf.boston2 <- randomForest(Boston.train, y = Y.train, xtest = Boston.test, ytest = Y.test, mtry = (ncol(Boston) - 1) / 2, ntree = 500)
rf.boston3 <- randomForest(Boston.train, y = Y.train, xtest = Boston.test, ytest = Y.test, mtry = sqrt(ncol(Boston) - 1), ntree = 500)
plot(1:500, rf.boston1$test$mse, col = "green", type = "l", xlab = "Number of Trees", ylab = "Test MSE", ylim = c(10, 19))
lines(1:500, rf.boston2$test$mse, col = "red", type = "l")
lines(1:500, rf.boston3$test$mse, col = "blue", type = "l")
legend("topright", c("m = p", "m = p/2", "m = sqrt(p)"), col = c("green", "red", "blue"), cex = 1, lty = 1)
```
## Problem 2

Problem 8 from Chapter 8 in the text. Set your seed with 9823 and split into 
train/test using 50\% of your data in each split. In addition to 
parts (a) - (e), do the following:

1. Fit a gradient-boosted tree to the training data and report the estimated 
test MSE. 
2. Fit a multiple regression model to the training data and report the 
estimated test MSE
3. Summarize your results. 

##Answer 2

####Part a
```{r}
set.seed(9823)
train <- sample(1:nrow(Carseats), nrow(Carseats), nrow(Carseats)/2)
train_carseats <- Carseats[train, ]
test_carseats <- Carseats[-train, ]
```

####Part b
```{r}
#Regression Tree
carseats_tree <- tree(Sales ~ ., data = train_carseats)
summary(carseats_tree)

plot(carseats_tree)
text(carseats_tree, pretty = 0)

pred_carseats <- predict(carseats_tree, newdata = test_carseats)
test_sales <- Carseats[-train, "Sales"]
mean((pred_carseats-test_sales)^2)
```

```{r}
#Gradient-Boosted Tree
train_carseats_gbm <- gbm(Sales ~ . ,data = train_carseats, distribution = "gaussian", n.trees = 5000, interaction.depth = 4)

summary(train_carseats_gbm)

par(mfrow = c(1,2))
plot(train_carseats_gbm, i = "Price")
plot(train_carseats_gbm, i = "ShelveLoc")

test_gbm_pred <- predict(train_carseats_gbm, newdata = test_carseats, n.trees = 5000)
mean((test_gbm_pred-test_sales)^2)

```

####Part c
```{r}
croVal_carseats <- cv.tree(carseats_tree)
plot(croVal_carseats$size, croVal_carseats$dev, type = "b")
tree_min <- which.min(croVal_carseats$dev)

carseat_prune <- prune.tree(carseats_tree, best = 5)
plot(carseat_prune)
text(carseat_prune,pretty = 0)

predict_carseats <- predict(carseats_tree, newdata = test_carseats)
plot(predict_carseats, test_sales)
abline(0, 1)
mean((predict_carseats-test_sales)^2)
```

####Part d
```{r}
carseats_bag <- randomForest(Sales ~ ., data = train_carseats, mtry = 10, ntree = 25, importance = TRUE)
predict_bag <- predict(carseats_bag, newdata = test_carseats)
mean((predict_bag-test_sales)^2)
importance(carseats_bag)
```

####Part e
```{r}
carseats_RF <- randomForest(Sales ~ ., data = train_carseats, mtry = 3, importance = TRUE)
predict_RF <- predict(carseats_RF, newdata = test_carseats)
mean((predict_RF - test_sales)^2)
importance(carseats_RF)
```